### 2016-07-04 sections/R20.0.tex

 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 2: 2D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
 \section{Two dimensional self-organizing maps}
 \label{sec: 2d_cluster}
    Although 1D networks are great to have a general idea about the data, neurons in 1D maps have maximum two neighbours, which causes some limitation in the results.
    In 2D networks, each neuron has two to six neighbours, which allowed them to to capture a whole picture of the complicated relations in the input data.
    Therefore, we created $10\times10$ 2D networks to study the data in details.
    As mentioned in previous sections, the size of SOMs are arbitrary and users must decide about it based on what their goals of using SOMs are.
    In this section we chose $10\times10$ size despite that we knew, from the size of our input data, that most of the neurons would be empty.
    Using 2D networks, we are mostly interested in the ability of the SOMs in showing underlying structure of the data rather than its clustering features.
    \import{../sections/image_texts/}{all.tex}
    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of M31 data.
    Similar to the Fig.~\ref{fig: M31_net_1by14}, all the 10 regions completely separated from each other in Fig.~\ref{fig: all_derived_ones}.

    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with very bright colour between their neurons, which presents that these two regions are very similar.
    Considering the position of these two regions in M31 (Both of these regions are right on the edge of the star forming rings in the galaxy), similarity of these two regions were predictable.
    Position of region 3 on the SOM is close to the position of regions 4 and 7, but with darker colour between the nodes. 
    In Fig.~\ref{fig: regions in m31} it is clear that, this region in M31 is closer to regions 4 and 7 than any other region, but it is on the outer side of the star forming ring.
    Regions 5 and 6 are in their second neighbourhood on the SOM, with a medium gray colour between them.
    These two regions are around the inner ring of the galaxy.
    Regions 8 and 6 are both in the inner ring of M31, but region 6 is in the region with more star forming activities, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.

    Regions 1 and 9 are close to each other, and in the same side of the star forming ring. 
    However, region 1 is in an area of the galaxy with lesser diffuse \halpha~emission than region 9, that might be the reason for their distances in SOM.
    Region 2 is more distant from other regions in the galaxy, and placed in the star forming ring.
    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffused \halpha~emission.
    Therefore, place of region 2 in the SOM is more favoured towards regions 1 and 4. 
    Region 10 is placed in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.

@@

    \subsection{Subsets}
    \label{sec: subsets}
            For analysing subsets, we creating SOMs by using only PAHs data, as well as using all data except PAHs ones (Fig.~\ref{fig: PAHS_or_not_PAHs}).
             \import{../sections/image_texts/}{PAHS_or_not_PAHs.tex}
            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, showed that the general position of regions in those networks are the same. 
            The region 10 is in one corner of the all three networks.
            However, in Fig.~\ref{fig: all_derived_ones} and Fig.~\ref{fig: wt_pahs}, region 10 is isolated from the other regions, while in Fig.~\ref{fig: only_pahs}, region 10 is much less isolated and only shows complete dissimilarity with region 8.
            Regions 9 and 10 are totally isolated in SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
            In both SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, there are dissimilarities between regions in M31 but in Fig.~\ref{fig: wt_pahs}, the colours are much darker than the ones in Fig.~\ref{fig: only_pahs}.
            This indicates that there are more similarity between PAHs features from all 10 regions then the other input data.

@@

            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to study effects of the input data on SOMs, further.
            Subset 1, that are listed in Tab.~\ref{tab: subset1}, includes all the inputs data except data from stellar mass.
            Tab.~\ref{tab: subset5} is the list of data that were used in a subset 2, which includes all data except the fact that instead of the individual PAH fluxes we added them all together and have total PAH flux. 
            For subset 3 ( in Tab.~\ref{tab: subset6}), we removed SPIRE 250 and 500~$\mu$m from subset 2.
            Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs that are created by data from subsets 1 to 3, respectively.
            The rest of the subsets are discussed in the Appendix.~\ref{sec: app_2d_soms_SOMN}.

            The results from Table~\ref{tab: subset1} is shown in Fig.~\ref{fig: subset1}. 
            In this SOM compare with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
            Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
            Since the differences in the amount of the stellar mass were one of the most distinct differences between these three regions, removing stellar mass from input data reduced the distance between these regions.
            Regions 5, 6 and 8 are in the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of the region 10.
            Distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.

@@

            Fig.~\ref{fig: subset6} shows the SOM generated from data that are listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except SPIRE 250 and 500~$\mu$m emission.
            Although for most of the regions we see the changes in their positions, the colours between neurons changed, too. 
            %Therefore, we can conclude that these changes caused by the differences in the initial assigned weights.
            The distance between the positions of the regions 4 and 2 are increased.
            The same happened for distances between regions 7, 3 and 6.
            In both cases, SPIRE 250 and 500~$\mu$m emission of these regions are similar to one another, and removing these two parameters from input data moved the positions of the regions further from each other. 
            \import{../sections/tables/}{subset6.tex}
            \import{../sections/image_texts/}{subset6.tex}

            %Subsets, that some of them  are studied in this section, can be used to learn about the effect of each input on the map as well as they can be used to predict unobserved quantities in the galaxy.
            \subsubsection{Prediction observing data using M31}

                On SOMs we can see relations between the input data from each region regarding to the other regions.
                These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
                Therefore, we have the probability distribution of quantities of each values given data from other regions.
                We can use these probability distribution to estimate missing data for regions.

                To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
                Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
                \import{../sections/image_texts/}{sim_subset1.tex}
                We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
                Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
                In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.

                We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
                \begin{equation}
                \label{equ: prob1}
                    P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
                \end{equation}
                Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
                We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
                This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.

    \subsection{Validating networks using M101 data}
    Another application of SOM for nearby galaxies is that to apply the trained networks on the data from other galaxies in order to prediction properties of the regions in them. %%eh
    As an example of this application, we generated an SOM using data from M31 that held in common with M101 data (Fig.~\ref{fig: subset9}a). 
    In this SOM, the same as the others, region 10 is separated from other regions in M31.
    Regions 7 and 4 are close to each other with very light colours between their neurons, and the same as the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
    \import{../sections/image_texts/}{subset9.tex}

    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a on M101 data (Fig.~\ref{fig: subset9}b).
    Region 6 in M31 and region 2 in M101 both occupied the same neuron in the network in Fig.~\ref{fig: subset9}, which immediately suggest that these two regions have similar properties. 
    Region 2 in M101 is a bright H {\sc II} region that is located at the end of the one of the M101 spiral arm (see Fig.~\ref{fig: regions in m101}). 
    Region 6 in M31 is located near the inner ring of the galaxy (see Fig.~\ref{fig: regions in m31}).
    Both regions have relatively low amount of PAHs emission and medium amount of the SFR regarding the other regions in the galaxy, which makes them very similar regions.

    Region 7 in M101 is located in the nucleus of the galaxy and have relatively higher quantities than the other regions.
    This region is located in the top right side of the network in Fig.~\ref{fig: subset9}, which is close to location of region 10 in the network.
    Since the bulge of a spiral galaxy has different environment from its nucleus, region 7 in M101 and region 10 in M31 are not occupied the same neuron in the SOM, and have a medium grey colour between their neurons.

@@

    In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
    We should note that we created our networks using values for 26 quantities from 10 regions in M31, which does not consider as a "big sample".
    Increasing dimension of the data and the number of regions would help to have more reliable networks.

>>>>

 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 2: 2D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
 \section{Two dimensional self-organizing maps}
 \label{sec: 2d_cluster}
    Although 1D networks are great to have a general idea about the data, neurons in 1D maps have maximum two neighbours, which causes some limitation in the results.
    In 2D networks, each neuron has two to six neighbours, which allowed them to to capture a whole picture of the complicated relations in the input data.
    Therefore, we created $10\times10$ 2D networks to study the data in details.
    As mentioned in previous sections, the size of SOMs are arbitrary and users must decide about it based on what their goals of using SOMs are.
    In this section we chose $10\times10$ size despite that we knew, from the size of our input data, that most of the neurons would be empty.
    Using 2D networks, we are mostly interested in the ability of the SOMs to showing underlying structure of the data rather than its clustering features.
    \import{../sections/image_texts/}{all.tex}
    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of M31 data.
    Similar to the Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.

    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with very bright colour between their neurons, which presents that these two regions are very similar.
    Considering the position of these two regions in M31 (Both of these regions are right on the edge of the star forming rings in the galaxy), similarity of these two regions were predictable.
    Position of region 3 on the SOM is close to the position of regions 4 and 7, but with darker colour between the nodes. 
    In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is closer to regions 4 and 7 than any other region, but it is on the outer side of the star forming ring.
    Regions 5 and 6 are in their second neighbourhood on the SOM, with a medium gray colour between them.
    These two regions are around the inner ring of the galaxy.
    Regions 8 and 6 are both in the inner ring of M31, but region 6 is in the region with more star formation, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.

    Regions 1 and 9 are close to each other, and in the same side of the star forming ring. 
    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, that might be the reason for their distances in SOM.
    Region 2 is more distant from other regions in the galaxy, and placed in the star forming ring.
    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
    Therefore, place of region 2 in the SOM is more favoured towards regions 1 and 4. 
    Region 10 is placed in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.

@@

    \subsection{Subsets}
    \label{sec: subsets}
            For analysing subsets, we creating SOMs by using only PAHs data, as well as using all data except PAHs ones (Fig.~\ref{fig: PAHS_or_not_PAHs}).
             \import{../sections/image_texts/}{PAHS_or_not_PAHs.tex}
            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs} shows that the general position of regions in those networks are the same. 
            Region 10 is in one corner of all three networks.
            However, in Fig.~\ref{fig: all_derived_ones} and Fig.~\ref{fig: wt_pahs}, region 10 is isolated from the other regions, while in Fig.~\ref{fig: only_pahs}, region 10 is much less isolated and only shows complete dissimilarity with region 8.
            Regions 9 and 10 are totally isolated in SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
            In both SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, there are dissimilarities between regions in M31 but in Fig.~\ref{fig: wt_pahs}, the colours are much darker than the ones in Fig.~\ref{fig: only_pahs}.
            This indicates that there are more similarity between PAHs features from all 10 regions then the other input data.

@@

            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to study effects of the input data on SOMs, further.
            Subset 1, that are listed in Tab.~\ref{tab: subset1}, includes all the inputs data except data from stellar mass.
            Tab.~\ref{tab: subset5} is the list of data that were used in a subset 2, which includes all data except the fact that instead of the individual PAH fluxes we added them all together and have total PAH flux. 
            For subset 3 ( in Tab.~\ref{tab: subset6}), we removed SPIRE 250 and 500~$\mu$m from subset 2.
            Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs that are created by data from subsets 1 to 3, respectively.
            The rest of the subsets are discussed in Appendix.~\ref{sec: app_2d_soms_SOMN}.

            The results from Table~\ref{tab: subset1} is shown in Fig.~\ref{fig: subset1}. 
            In this SOM compared with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
            Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
            Since the differences in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from input data reduced the distance between these regions.
            Regions 5, 6 and 8 are in the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of region 10.
            Distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.

@@

            Fig.~\ref{fig: subset6} shows the SOM generated from data that are listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except SPIRE 250 and 500~$\mu$m emission.
            Although for most of the regions we see the changes in their positions, the colours between neurons changes as well. 
            %Therefore, we can conclude that these changes caused by the differences in the initial assigned weights.
            The distance between the positions of the regions 4 and 2 are increased.
            The same happened for distances between regions 7, 3 and 6.
            In both cases, SPIRE 250 and 500~$\mu$m emission of these regions are similar to one another, and removing these two parameters from input data moved the positions of the regions further from each other. 
            \import{../sections/tables/}{subset6.tex}
            \import{../sections/image_texts/}{subset6.tex}

            %Subsets, that some of them  are studied in this section, can be used to learn about the effect of each input on the map as well as they can be used to predict unobserved quantities in the galaxy.

            % \subsubsection{Prediction observing data using M31}

            %     On SOMs we can see relations between the input data from each region regarding to the other regions.
            %     These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
            %     Therefore, we have the probability distribution of quantities of each values given data from other regions.
            %     We can use these probability distribution to estimate missing data for regions.

            %     To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
            %     Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
            %     \import{../sections/image_texts/}{sim_subset1.tex}
            %     We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
            %     Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
            %     In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.

            %     We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
            %     \begin{equation}
            %     \label{equ: prob1}
            %         P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
            %     \end{equation}
            %     Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
            %     We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
            %     This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.

    \subsection{Testing networks using M101 data}
    Another application of SOM for nearby galaxies is to apply the trained networks on the data from other galaxies in order to predict properties of the observed regions in them. %%eh
    Therefore, we generated an SOM using data from M31 that hold in common with M101 data (Fig.~\ref{fig: subset9}a). 
    \cite{Dim15} compared PAHs in M31 with those from H {\sc II} regions in M101, and showed the similarity between PAHs from these two galaxies (For more detail see \cite{Dim15} and \cite{Gordon08}).
    In this SOM, the same as the others, region 10 is separated from other regions in M31.
    Regions 7 and 4 are close to each other with very light colours between their neurons, and the same as the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
    \import{../sections/image_texts/}{subset9.tex}

    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a on M101 data (Fig.~\ref{fig: subset9}b).
    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggest that these regions have similar properties.

    Region 2 in M101 is a bright H {\sc II} region that is located at the end of the one of the M101 spiral arm (see Fig.~\ref{fig: regions in m101}). 
    Region 6 in M31 is located near the inner ring of the galaxy (see Fig.~\ref{fig: regions in m31}).
    Both regions have relatively low amount of PAHs emission and medium amount of the SFR regarding the other regions in the galaxy, which makes them very similar regions.

    Region 5 in M31 is in inner ring of the galaxy and it is one of two regions in M31 that are not an  H {\sc II} region.
    region 8 in M101 is in a spiral arm of the galaxy.
    Relatively low stellar mass, SFR and SPIRE band emission caused these two regions have close distance in the map.
    In Sec.~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties, in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101. 
    These regions all have medium or low amount of PAHs, dust and SFR compare to the rest of them.

    Region 7 in M101 is located in the nucleus of the galaxy and has relatively higher quantities than the other regions.
    This region is located in the top right side of the network in Fig.~\ref{fig: subset9}, which is close to location of region 10 in the network.
    Since the bulge of a spiral galaxy has different environment from its nucleus, region 7 in M101 and region 10 in M31 are not occupied the same neuron in the SOM, and have a medium grey colour between their neurons.

@@

    Knowing effect of each data entry on the networks From Section~\ref{sec: subsets}, we can have ideas about that data entry that we do
    In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
    We should note that, since we normalized data before using them in the networks, we only see a relative properties of the regions.
    Therefore, we need data from few regions in the galaxy to use this network cannot use these networks to learn about properties of a single region in other galaxies.

### 2016-07-04 sections/intro0.0.tex

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction} %%( I am not really happy with this introduction but it is the best I can have for now:/ )
%General information about galaxies %(Maybe it is too generic?!!)
Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
Galaxies are an active and complicated systems, that are constantly changing.
There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.

% Nearby galaxies and their importance 
Nearby galaxies play an important role in learning about galaxies' formation and evolution.
These galaxies are close enough to be able to observe various regions inside them in details.
As a result, many studies are devoted to find relations between physical properties of the galaxies in both spatially resolved regions and galaxies as a whole%(Some more references here)
, and many others use these results in analyzing data from high-redshift galaxies. %(Some more references here)
The amount of data that is acquired from nearby galaxies is increasing daily.
Advances in technology helps to both observe and store enormous amount of data from sky.%The sky?! 
Telescopes and surveys gather data from nearby galaxies in variuse wavelengths and from these data we can measure physical properties of galaxies (e.g. stellar mass, star formation rate (SFR), dust mass, gas mass)~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), with a distance of $\sim$0.78~Mpc~\citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
Images of this galaxy provide us a detail view of inside of a spiral galaxy from distance.
M31 data was a target of many telescopes (e.g. {\it Hubble} \citep{Dalcanton12}, \Spitzer\citep{Wener04}, \Herschel\citep{Pilbratt10} space telescopes) and was a subject of many more studies \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.

\cite{Barmby06} used data from Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show evidence of Polycyclic Aromatic Hydrocarbons (PAH)s in interstellar medium (ISM) of M31.
Using the mid-IR data from Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of the dust in M31.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used spectroscopic data of the galaxy to study PAHs and other line emissions in the ISM.

@@

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} wrote an extensive review of data mining and machine learning, and their usages in astronomy.
A data mining algorithm learns about data from sets of trainings, which can be supervised or unsupervised.
The supervised trainings refer to methods, that use examples of the desired output to learn about input data and are valuable tools to classify data with known target values.
On the contrary, the unsupervised methods train without any prior knowledge of output results. 
They solely work based on the underlying structure of input data.   
The unsupervised methods are very useful tools in knowledge discovery studies on input data, which we do not have any insight of them (or when we want to make sure that we did not miss any valuable information in our previous studies). %%% ehh to after or part.

%SOM
One the most tested methods of data mining in astronomy is the artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein12, Hossein14,Hossein16,Ellison16a}.
ANNs are designed to work in the same way that the neurons work in a human mind.
They are networks of interconnected neurons (nodes), which all of the connections are weighted.
These networks are used to study about nonlinear and complex relations between input and output data.
%These relations can be applied to the new sets of data with similar feature

@@

% other Unsupervised methods
The purpose of this project is to have a new insight into nearby galaxies using M31 data with focusing on relations between PAHs and other properties of the galaxy.
To fulfill this purpose, an unsupervised data mining method is the most suitable choice. %%eh  
K-means algorithm, SOMs, and hierarchical clustering are main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more

For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of the clusters.
In the hierarchical clustering method, the user must define dissimilarity between the groups, and the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure. 
Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method miss-classifies the data~\citep[][and references therein]{Mangiameli96}.
We chose SOM method over K-means due to the fact that SOMs not only clusters data, but also shows similarity and dissimilarity between each cluster.
Therefore, we can cluster our sample data and study the underlying structure of data, simultaneously.

%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
In this project we apply SOM algorithm on M31 data, and trained 1D and 2D networks.
Using smaller size networks we study the properties of the clusters and investigate relations between PAHs features with other features in M31.
We create 2D SOMs from subsets of data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM, which leads to prediction of the unmeasured quantities in a galaxy.
Assuming that all the spiral nearby galaxies have similar properties, we apply 2D trained networks on data from the Pinwheel Galaxy (M101), which is another spiral nearby galaxy. 
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.

In Section $\S$~\ref{Sec: data_SOMN}, we present the sample data from M31 and M101, that we use in this study. 
We describe the SOM method in Section $\S$~\ref{sec: method}. 
The results of the 1D SOM networks and studying PAHs in M31 is presented in Section $\S$~\ref{Sec: 1d_cluster}.
In Section $\S$~\ref{sec: 2d_cluster}, we present the result of 2D SOM networks and how we use them to extract information about other galaxies.
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.

>>>>

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction} %%( I am not really happy with this introduction but it is the best I can have for now:/ )
%General information about galaxies %(Maybe it is too generic?!!)
% Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
% Galaxies are an active and complicated systems, that are constantly changing.
% There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
% These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.

% Nearby galaxies and their importance 
Nearby galaxies play an important role in learning about galaxies' formation and evolution.
These galaxies are close enough to be able to observe various regions inside them in detail.
As a result, many studies are devoted to find relations between physical properties of the galaxies in both spatially resolved regions and galaxies as a whole%(Some more references here)
, and many others use these results in analyzing data from high-redshift galaxies. %(Some more references here)
The amount of data that is acquired from nearby galaxies is increasing daily.
Advances in technology helps to both observe and store enormous amount of data from sky.%The sky?! 
Telescopes and surveys gather data from nearby galaxies in various wavelengths and from these data we can measure physical properties of galaxies (e.g. stellar mass, star formation rate (SFR), dust mass, gas mass)~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), with a distance of $\sim$0.78~Mpc~\citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
Images of this galaxy provide us a detail view of inside of a spiral galaxy from distance.
M31 was a target of many telescopes (e.g. {\it Hubble} \citep{Dalcanton12}, \Spitzer\citep{Wener04}, \Herschel\citep{Pilbratt10} space telescopes) and was a subject of many more studies. % \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.

\cite{Barmby06} used data from Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to how evidence of Polycyclic Aromatic Hydrocarbons (PAH)s in interstellar medium (ISM) of M31.
%or to study the stellar and nonstellar mid-infrared (MIR) emission in M31. ?! 
Using the mid-IR data from Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of the dust in M31.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used spectroscopic data the galaxy to study PAHs and other line emission in the ISM.

@@

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} wrote an extensive review of data mining and machine learning, and their usage in astronomy.
A data mining algorithm learns about data from sets of trainings, which can be supervised or unsupervised.
The supervised training refer to methods that use examples of the desired output to learn about input data and are valuable tools to classify data with known target values.
On the contrary, the unsupervised methods train without any prior knowledge of output results. 
They work solely based on the underlying structure of input data.   
The unsupervised methods are very useful tools in knowledge discovery studies on input data, which we do not have any insight of them (or when we want to make sure that we did not miss any valuable information in our previous studies). %%% ehh to after or part.

%SOM
One the most tested methods of data mining in astronomy is the artificial neural networks (ANNs)~\citep[e.g.][and references therein]{ Hossein14,Hossein16}.
ANNs are designed to work in the same way that the neurons work in a human brain.
They are networks of interconnected neurons (nodes), which all of the connections are weighted.
These networks are used to study about nonlinear and complex relations between input and output data.
%These relations can be applied to the new sets of data with similar feature

@@

 %%add a little bit about PAHs in M31, dim15, drain14 and refs. therein. talk about what questions are still remained unanswered.
The purpose of this project is to have a new insight into nearby galaxies using M31 data with focusing on relations between PAHs and other properties of the galaxy.
There are very few studies on relations between properties of M31 with its PAH features.
To fulfill this purpose, an unsupervised data mining method is the most suitable choice.
\cite{Cesarsky98} studied PAH spectra in four regions in M31 and showed that PAH features in M31 differ from the PAH spectra in other galaxies; in the way that there are  week or no 6.2 - 8.6~$\mu$m with enhanced 11.2~$\mu$m emission in M31 spectra. 
However, \cite{Dim15} by using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations indicate that the PAH spectra of M31 has the same features as spectra of other nearby star forming galaxies.
Using MIR photometry data of M31,\cite{Barmby06} compared the observed 8~$\mu$m luminosity with other star formation indicators in the galaxy and found good agreements among them, and \cite{Draine14} found the PAH abundance in M31 is almost constant up to R$\sim 20$~Kpc.
Therefore, using data mining techniques, we aim to study PAH features in more detail.

K-means algorithm, SOMs, and hierarchical clustering are main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of the clusters.
In the hierarchical clustering method, the user must define dissimilarity between the groups, the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure. 
Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method miss-classifies the data~\citep[][and references therein]{Mangiameli96}.
We chose SOM method over K-means due to the fact that SOMs not only cluster data, but also show similarity and dissimilarity between each cluster.
Therefore, we can cluster our sample data and study the underlying structure, simultaneously.

%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
In this project we apply SOM algorithm on M31 data, and trained 1D and 2D networks.
Using smaller networks we study the properties of the clusters and investigate relations between PAH features with other quantities in M31.
We create 2D SOMs from subsets of data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM.%, which leads to prediction of the unmeasured quantities in a galaxy.
We apply 2D trained networks on data from the Pinwheel Galaxy (M101), which is a spiral nearby galaxy, to check weather that all the spiral nearby galaxies have similar properties,
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.

In Section $\S$~\ref{Sec: data_SOMN}, we present the sample data from M31 and M101 that we use in this study. 
We describe the SOM method in Section $\S$~\ref{sec: method}. 
The results of the 1D SOM networks and studying PAHs in M31 is presented in Section $\S$~\ref{Sec: 1d_cluster}.
In Section $\S$~\ref{sec: 2d_cluster}, we present the result of 2D SOM networks and how we use them to extract information about other galaxies.
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
